Outline

### 2020-07-09 Outline.Rmd
Update Outline.Rmd
Adding landscape genetics to outline

- Base R
- Basic spatial data
    - Basic data types (i.e. vector vs. raster data)
        - raster, stars, terra(?)
        - sp (+rgeos, rgdal), sf
        - ...
- Creating maps
    - tmap, ggplot2
    - mapview, leaflet
    - ...
- Spatial regression
    - nlme
    - spdep, gstat/geoR (spatial autocorrelation), + pgirmess??, (http://www.r-inla.org/download; INLA?? check license)
    - ...
- Spatial statistics?? (point-patterns analysis) // MH:I think that's way too much
    - spatstat (e.g., https://link.springer.com/chapter/10.1007/978-3-030-01989-1_4)
- Ecological analysis
    - Landscape metrics
        - landscapmetrics
        - belg
        - ...
    - Habitat selection and SDM
        - https://link.springer.com/chapter/10.1007/978-3-030-01989-1_7
        - lm(), glm(), gam, rpart, RandomForest (ranger), lme4
        - ade4, adehabitat, sdm
        - some MAXENT package?
        - biomod2??
        - ...
    - Connectivity? 
        - https://link.springer.com/chapter/10.1007/978-3-030-01989-1_9
        - gdistance??
    - Spatial population dynamics
        - https://link.springer.com/chapter/10.1007/978-3-030-01989-1_10
    - Various
        - vegan
        - dismo
        - NLMR (and RandomFields), landscapetools
        - ecospat?? (https://onlinelibrary.wiley.com/doi/full/10.1111/ecog.02671)
        - PresenceAbsence?? (https://www.jstatsoft.org/article/view/v023i11)
        - ENMeval?? (https://cran.r-project.org/web/packages/ENMeval/index.html)
        - prioritizr?? (https://prioritizr.net/)
        - data sources/API connections?
        - ecodist?? (https://cran.r-project.org/web/packages/ecodist/index.html)
        - LEA?? (http://membres-timc.imag.fr/Olivier.Francois/Frichot_etal_MEE_2015.pdf)
        - remote sensing??
        - agent-based modelling // MH:I think that's way too much
    - ...
- ...
### 3. Missing packages
- First topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- Second topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- ...
- Last topic (often objectives and hypotheses)
    - ...

>>>>

- Base R
- Basic spatial data
    - Basic data types (i.e. vector vs. raster data)
        - raster, stars, terra(?)
        - sp (+rgeos, rgdal), sf
        - Access to spatial data (e.g. rnaturalearth) (?)
        - ...
- Creating maps
    - tmap, ggplot2
    - mapview, leaflet
    - ...
- Spatial regression
    - nlme
    - spdep, gstat/geoR (spatial autocorrelation), + pgirmess??, (http://www.r-inla.org/download; INLA?? check license)
    - ...
- Spatial statistics?? (point-patterns analysis) // MH:I think that's way too much
    - spatstat (e.g., https://link.springer.com/chapter/10.1007/978-3-030-01989-1_4)
- Ecological analysis
    - Landscape metrics
        - landscapmetrics
        - belg
        - ...
    - Habitat selection and SDM
        - https://link.springer.com/chapter/10.1007/978-3-030-01989-1_7
        - lm(), glm(), gam, rpart, RandomForest (ranger), lme4
        - ade4, adehabitat, sdm
        - some MAXENT package?
        - biomod2??
        - ...
    - Connectivity? 
        - https://link.springer.com/chapter/10.1007/978-3-030-01989-1_9
        - gdistance??
    - Spatial population dynamics
        - https://link.springer.com/chapter/10.1007/978-3-030-01989-1_10
    - Landscape genetics
    - Various
        - vegan
        - dismo
        - NLMR (and RandomFields), landscapetools
        - ecospat?? (https://onlinelibrary.wiley.com/doi/full/10.1111/ecog.02671)
        - PresenceAbsence?? (https://www.jstatsoft.org/article/view/v023i11)
        - ENMeval?? (https://cran.r-project.org/web/packages/ENMeval/index.html)
        - prioritizr?? (https://prioritizr.net/)
        - data sources/API connections?
        - ecodist?? (https://cran.r-project.org/web/packages/ecodist/index.html)
        - LEA?? (http://membres-timc.imag.fr/Olivier.Francois/Frichot_etal_MEE_2015.pdf)
        - remote sensing??
        - agent-based modelling // MH:I think that's way too much
    - ...
- ...
### 3. Missing packages
- First topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- Second topic
    - First paragraph headline
    - Second paragraph headline
    - ...
- ...
- Last topic (often objectives and hypotheses)
    - ...
